No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-07 R/MSE manuscript.Rmd
Fis all strsplit by changing "," to ", "; remove uneccessary funs() from summarise_all calls; Add grey circle around points in the map; comment out part.data$order specification

freq.data_pub<-data_pub %>%
    select(all_of(freq.col)) %>%
    rename("Process"="ProcessExplicit",
           "Problem"="ProblemDefinitionExplicit",
           "Objectives"="ObjectivesExplicit",
           "Alternatives"="AlternativesExplicit",
           "Tradeoffs"="TradeOffsExplicit",
           "Decision"="DecisionExplicit",
           "Results Adopted"="ResultsAdopted") %>%
    summarise_all(funs(sum))%>%
    gather(Explicit) %>%
    mutate(Percent=value/n_pub*100) %>%
    mutate(Explicit=factor(Explicit,levels=
                  c("Process","Problem","Objectives","Alternatives","Tradeoffs","Decision","Results Adopted"))) %>%
    rename("Number"="value")

freq.data_CC<-data_CC %>%
  select(all_of(freq.col)) %>%
  rename("Process"="ProcessExplicit",
         "Problem"="ProblemDefinitionExplicit",
         "Objectives"="ObjectivesExplicit",
         "Alternatives"="AlternativesExplicit",
         "Tradeoffs"="TradeOffsExplicit",
         "Decision"="DecisionExplicit",
         "Results Adopted"="ResultsAdopted") %>%
  summarise_all(funs(sum))%>%
  gather(Explicit) %>%
  mutate(Percent=value/n_CC*100) %>%
  mutate(Explicit=factor(Explicit,levels=
                           c("Process","Problem","Objectives","Alternatives","Tradeoffs","Decision","Results Adopted"))) %>%
  rename("Number"="value")

freq2.data_pub<-data_pub %>%
    select(all_of(freq2.col)) %>%
    rename("Roles"="RoleSpecification",
           "Open Meetings"="OpenMeetings") %>%
    summarise_all(funs(sum)) %>%
    gather(Explicit) %>%
    mutate(Percent=value/n_pub*100) %>%
    mutate(Explicit=factor(Explicit,levels=
                  c("Roles","Open Meetings"))) %>%
    rename("Number"="value")

@@

# What drivers are considered
drive.data_pub<-data_pub %>%
    select(Drivers) %>%
    purrr::map(~ strsplit(as.character(.),split=",")) %>%
    purrr::map(unlist) %>%
    purrr::map(table) %>%
    plyr::ldply(data.frame) %>%
    select(Var1,Freq) %>%
    rename("Driver"="Var1","Frequency"="Freq") %>%
    mutate(Percent=Frequency/n_pub*100) %>%
    arrange(desc(Frequency))

drive.data_CC<-data_CC %>%
  select(Drivers) %>%
  purrr::map(~ strsplit(as.character(.),split=",")) %>%
  purrr::map(unlist) %>%
  purrr::map(table) %>%
  plyr::ldply(data.frame) %>%
  select(Var1,Freq) %>%
  rename("Driver"="Var1","Frequency"="Freq") %>%
  mutate(Percent=Frequency/n_CC*100) %>%
  arrange(desc(Frequency))

@@

# What Alternative types are considered
altcat.data_pub<-alt.data_pub %>%
    select(ManagementType) %>%
    purrr::map(~ strsplit(as.character(.),split=",")) %>%
    purrr::map(unlist) %>%
    purrr::map(table) %>%
    plyr::ldply(data.frame) %>%
    select(Var1,Freq) %>%
    rename("Management Type"="Var1","Number"="Freq") %>%
    mutate(Percent=round(Number/n_pub*100,0)) %>%
    mutate('Per MSE'=round(Number/n_pub,2)) %>%
    arrange(desc(Number))

@@

# label MSEs articles by analysis for ploting
freq.data_pub<-mutate(freq.data_pub,Analysis="Random Sample")
freq.data_CC<-mutate(freq.data_CC,Analysis="Climate Change")
freq.data<-rbind(freq.data_pub,freq.data_CC)
part.data_pub<-mutate(part.data_pub,Analysis="Random Sample")
part.data_CC<-mutate(part.data_CC,Analysis="Climate Change")
part.data<-rbind(part.data_pub,part.data_CC) %>% 
  arrange(Stage, Percent) %>% 
  mutate(order = row_number())
part.data$order<-c(1,2,3,3,4,4,5,6,7,8,6,9,10,8,9,11,12,10,13,12,13,14,14,15,16,17,18,19,20,
                   16,17,18,20,21,22,23,24,25,21,23,26,25,26,27,27,28,29,30,31,29,32,30,33,
                   32,33,34,35,36,37,38,39,39)
drive.data_pub<-mutate(drive.data_pub,Analysis="Random Sample") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data_CC<-mutate(drive.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data<-rbind(drive.data_pub,drive.data_CC) %>% 
  arrange(Percent) %>%
  mutate(order = row_number())
drive.data$order<-c(6,5,4,3,2,1,8,7,12,9,3,15,14,13,12,11,10,14,16,15,
                   16,6)
# Wrangle objective category data by Random Sample, climate change, and combined
objcat.data_pub<-mutate(objcat.data_pub,Analysis="Random Sample") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,'Objective Category',Percent,Frequency)
objcat.data_CC<-mutate(objcat.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,'Objective Category',Percent,Frequency)
objcat.data<-rbind(objcat.data_pub,objcat.data_CC) %>% 
  rename(OC='Objective Category') %>% 
  arrange(OC) %>% 
  rename('Objective Category'=OC)

@@

# plot MSEs on map
MSE.map<-ggplot(data=map.data,aes(x=Longitude, y=Latitude,color=Drivers)) + world +
  geom_point(size=2.5) + scale_color_manual(values=c("#66CCCC","#006666")) +  theme_void() +
  theme(legend.position = c(0.15, 0.25))

>>>>

freq.data_pub<-data_pub %>%
    select(all_of(freq.col)) %>%
    rename("Process"="ProcessExplicit",
           "Problem"="ProblemDefinitionExplicit",
           "Objectives"="ObjectivesExplicit",
           "Alternatives"="AlternativesExplicit",
           "Tradeoffs"="TradeOffsExplicit",
           "Decision"="DecisionExplicit",
           "Results Adopted"="ResultsAdopted") %>%
    summarise_all(sum)%>%
    gather(Explicit) %>%
    mutate(Percent=value/n_pub*100) %>%
    mutate(Explicit=factor(Explicit,levels=
                  c("Process","Problem","Objectives","Alternatives","Tradeoffs","Decision","Results Adopted"))) %>%
    rename("Number"="value")

freq.data_CC<-data_CC %>%
  select(all_of(freq.col)) %>%
  rename("Process"="ProcessExplicit",
         "Problem"="ProblemDefinitionExplicit",
         "Objectives"="ObjectivesExplicit",
         "Alternatives"="AlternativesExplicit",
         "Tradeoffs"="TradeOffsExplicit",
         "Decision"="DecisionExplicit",
         "Results Adopted"="ResultsAdopted") %>%
  summarise_all(sum)%>%
  gather(Explicit) %>%
  mutate(Percent=value/n_CC*100) %>%
  mutate(Explicit=factor(Explicit,levels=
                           c("Process","Problem","Objectives","Alternatives","Tradeoffs","Decision","Results Adopted"))) %>%
  rename("Number"="value")

freq2.data_pub<-data_pub %>%
    select(all_of(freq2.col)) %>%
    rename("Roles"="RoleSpecification",
           "Open Meetings"="OpenMeetings") %>%
    summarise_all(sum) %>%
    gather(Explicit) %>%
    mutate(Percent=value/n_pub*100) %>%
    mutate(Explicit=factor(Explicit,levels=
                  c("Roles","Open Meetings"))) %>%
    rename("Number"="value")

@@

# What drivers are considered
drive.data_pub<-data_pub %>%
    select(Drivers) %>%
    purrr::map(~ strsplit(as.character(.),split=", ")) %>%
    purrr::map(unlist) %>%
    purrr::map(table) %>%
    plyr::ldply(data.frame) %>%
    select(Var1,Freq) %>%
    rename("Driver"="Var1","Frequency"="Freq") %>%
    mutate(Percent=Frequency/n_pub*100) %>%
    arrange(desc(Frequency))

drive.data_CC<-data_CC %>%
  select(Drivers) %>%
  purrr::map(~ strsplit(as.character(.),split=", ")) %>%
  purrr::map(unlist) %>%
  purrr::map(table) %>%
  plyr::ldply(data.frame) %>%
  select(Var1,Freq) %>%
  rename("Driver"="Var1","Frequency"="Freq") %>%
  mutate(Percent=Frequency/n_CC*100) %>%
  arrange(desc(Frequency))

@@

# What Alternative types are considered
altcat.data_pub<-alt.data_pub %>%
    select(ManagementType) %>%
    purrr::map(~ strsplit(as.character(.),split=", ")) %>%
    purrr::map(unlist) %>%
    purrr::map(table) %>%
    plyr::ldply(data.frame) %>%
    select(Var1,Freq) %>%
    rename("Management Type"="Var1","Number"="Freq") %>%
    mutate(Percent=round(Number/n_pub*100,0)) %>%
    mutate('Per MSE'=round(Number/n_pub,2)) %>%
    arrange(desc(Number))

@@

# label MSEs articles by analysis for ploting
freq.data_pub<-mutate(freq.data_pub,Analysis="Random Sample")
freq.data_CC<-mutate(freq.data_CC,Analysis="Climate Change")
freq.data<-rbind(freq.data_pub,freq.data_CC)
part.data_pub<-mutate(part.data_pub,Analysis="Random Sample")
part.data_CC<-mutate(part.data_CC,Analysis="Climate Change")
part.data<-rbind(part.data_pub,part.data_CC) %>% 
  arrange(Stage, Percent) %>% 
  mutate(order = row_number())
# part.data$order<-c(1,2,3,3,4,4,5,6,7,8,6,9,10,8,9,11,12,10,13,12,13,14,14,15,16,17,18,19,
#                    20,16,17,18,20,21,22,23,24,25,21,23,26,25,26,27,27,28,29,30,31,29,32,
#                    30,33,32,33,34,35,36,37,38,39,39)
drive.data_pub<-mutate(drive.data_pub,Analysis="Random Sample") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data_CC<-mutate(drive.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data<-rbind(drive.data_pub,drive.data_CC) %>% 
  arrange(Percent) %>%
  mutate(order = row_number())
drive.data$order<-c(6,5,4,3,2,1,8,7,12,9,3,15,14,13,12,11,10,14,16,15,
                   16,6)
# Wrangle objective category data by Random Sample, climate change, and combined
objcat.data_pub<-mutate(objcat.data_pub,Analysis="Random Sample") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,'Objective Category',Percent,Frequency)
objcat.data_CC<-mutate(objcat.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,'Objective Category',Percent,Frequency)
objcat.data<-rbind(objcat.data_pub,objcat.data_CC) %>% 
  rename(OC='Objective Category') %>% 
  arrange(OC) %>% 
  rename('Objective Category'=OC)

@@

# plot MSEs on map
MSE.map<-ggplot(data=map.data,aes(x=Longitude, y=Latitude,color=Drivers)) + world +
  geom_point(size=2.5) + geom_point(size = 2.5, colour = "grey", shape = 1) +
  scale_color_manual(values=c("#66CCCC","#006666"))+theme_void() +
  theme(legend.position = c(0.15, 0.25))
